LSOA domestic Electricty and Gas maps

### 2021-09-06 LSOA domestic Elec and Gas.Rmd
comparing absolute change with % change

>>>>

nrow(Solent)
```
Plot kWh change as a contrast to % change (which seems constant-ish across IMD)

```{r plotkWhchange}
# as a contrast to % change

ggplot(Solent, aes(x = mean_de2010, # forces a box plot at each value 
                   y =mean_de_diff,
                   colour = la_name)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Domestic mean kWh 2010",
       y = "Change in mean domestic kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ .)

ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =mean_de_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs")

# or without colour but using facets for Local Authorities
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =mean_de_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ .)

nrow(Solent)
```
So there is a slightly downward trend - those in lower deprivation deciles are reducing slightly more.
